Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-10-26 paper/main.tex
Author list update
Fixed author typo
WJC - updated Table 3

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Tanda Li,$^{1,2}$
Guy R. Davies,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
and To B. Confirmed
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
}

@@

\begin{table}
	\centering
	\caption{The median error, $\mu_{1/2}$ and median absolute deviation of the error, $\sigma_\mathrm{MAD} = 1.4826\cdot\mathrm{median}(|E(x) - \mu_{1/2}|)$, for each output, $x$, where $E(x)$ is the error given in the first column and $\delta x = x_\mathrm{pred} - x_\mathrm{true}$. All parameters are outputs of the ANN except for $L$ which is derived.}
	\label{tab:validation}
    \input{validation}    
\end{table}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Oliver J. Hall,
Hin Leung,
Harry Westwood,
William J. Chaplin,$^{1,2}$
Daniel Huber,
\newauthor
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
and To B. Confirmed
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
}

@@

\begin{table}
	\centering
	\caption{The median error, $\mu_{1/2}$ and median absolute deviation of the error, $\sigma_\mathrm{MAD} = 1.4826\cdot\mathrm{median}(|E(x) - \mu_{1/2}|)$ for a given parameter, $x$, derived from the output of the ANN. The error, $E(x)$, is given in the first column and $\delta x$ is the truth provided by the validation dataset subtracted from the ANN prediction. Fractional errors are given as percentages (\%).}
	\label{tab:validation}
    \input{validation}    
\end{table}
